### 2019-04-01 0_abstract.tex
apply some of George's comments

We conduct a comprehensive study with implementations of Task Bench in
13 programming systems on up to 256 Haswell nodes of the Cori
supercomputer. We use a novel metric, \emph{minimum effective task
  granularity} to study the baseline runtime overhead of each system
and the impact of different dependence patterns. We also
study each system's scalability, and ability to hide communication and
mitigate load imbalance.
\end{abstract}

>>>>

We conduct a comprehensive study with implementations of Task Bench in
13 programming systems on up to 256 Haswell nodes of the Cori
supercomputer. We introduce and use a novel metric, \emph{minimum effective task
  granularity} to study the baseline runtime overhead of each system
and the impact of different dependence patterns. We also
study each system's scalability, and ability to hide communication and
mitigate load imbalance.
\end{abstract}

### 2019-04-01 1_introduction.tex
apply some of George's comments

One approach to comparing the performance of different systems has
focused on the development of \emph{proxy-} or
\emph{mini-apps}. Because they distill the structure of a larger
application, mini-apps can provide insight
without the expense of developing a full-blown
application. However, despite the name, our experience is that
mini-apps still requite significant investment to develop, especially
to the level of quality needed for useful benchmarking. In many cases,
the effort to tune for performance exceeds the effort to develop the
mini-app in the first place. As a result, implementations of mini-apps
often do not reach the level of maturity required to compare
systems. Indeed, there are few such published studies that involve
more than a handful of systems.

@@

To address the second issue and isolate the contribution of the programming model's runtime system
to application performance, we introduce a new metric called
\emph{minimum effective task granularity} (METG). Intuitively,
METG(50\%) is the smallest application task granularity which can be
executed while maintaining at least 50\% computational efficiency,
meaning that the application achieves at least 50\% of peak
performance on a given machine. METG captures the essence of what is important in a weak
or strong scaling study, the behavior at the limit of scalability. For
weak scaling, METG(50\%) corresponds directly to the smallest problem
size that can be weak scaled with 50\% efficiency. For strong scaling,
METG(50\%) can be used to compute the scale at which performance can
be expected to dip below 50\% efficiency.

>>>>

One approach to comparing the performance of different systems has
focused on the development of \emph{proxy-} or
\emph{mini-apps}. Because they distill the structure of a larger
application, mini-apps can provide insight
without the expense of developing a full-blown
application. However, despite the name, our experience is that
mini-apps still requite significant investment to develop, especially
to the level of quality needed for useful benchmarking. In many cases,
the effort to tune for performance exceeds the effort to develop the
mini-app in the first place. As a result, implementations of mini-apps
often do not reach the level of maturity required to compare
systems. Indeed, there are few such published studies~\cite{LULESH13, PRK14, NAS95}
that involve more than a handful of systems.

@@

To address the second issue and isolate the contribution of the programming model's runtime system
to application performance, we introduce a new metric called
\emph{minimum effective task granularity} (METG). Intuitively,
METG(50\%) is the smallest application task granularity which can be
executed while maintaining at least 50\% efficiency,
meaning that the application achieves at least 50\% of peak
performance in terms of FLOPS, memory or IO bandwidth 
on a given machine. METG captures the essence of what is important in a weak
or strong scaling study, the behavior at the limit of scalability. For
weak scaling, METG(50\%) corresponds directly to the smallest problem
size that can be weak scaled with 50\% efficiency. For strong scaling,
METG(50\%) can be used to compute the scale at which performance can
be expected to dip below 50\% efficiency.

### 2019-04-01 5_evaluation.tex
Tweaks to the paper.
apply some of George's comments

Figure~\ref{fig:efficiency} shows efficiency (as a percentage of
peak FLOPS achieved) plotted against task granularity. This plot is
used to calculate METG(50\%), as described in Section~\ref{sec:metg}. The
red, dashed line shows the point where 50\% efficiency is achieved.

@@

Implicitly parallel systems such as PaRSEC, StarPU and Regent that
rely on runtime analysis to build the DAG can suffer from
scalability bottlenecks if every node must consider the tasks
executing on all other nodes. PaRSEC DTD and StarPU mitigate this
partially by allowing the user to omit tasks that are not direct
dependencies of those executed on the current node. However, this DAG
trimming approach still requires some dynamic checks that scale with
the number of nodes and thus limits scalability. Approaches based on compile-time analysis can
partially or fully mitigate this overhead. PaRSEC PTG improves over DTD by performing DAG expansion at compile time, but
still retains dynamic checks leading to limited scalability. Regent
uses a compile-time optimization that enables full horizontal
scalability~\cite{ControlReplication17}. A similar, manual
optimization is shown in the plots as PaRSEC DTD Shard.

@@

The difference between the remaining systems is due primarily to the
scheduling behavior of the various systems. The execution of 4
simultaneous task graphs partially, but does not fully, mitigate the
load imbalance in the tasks. Therefore, systems which provide an
additional on-node work stealing capability see additional gains in
efficiency at large task granularities. However, the use of
work-stealing queues can also impact throughput at very small task
granularities. This can be seen in the difference between Chapel
Distrib (which uses a work stealing scheduler) vs Chapel with its
default (non-work-stealing) scheduler.

>>>>

Figure~\ref{fig:efficiency} shows efficiency (as a percentage of
peak FLOPS) plotted against task granularity. This plot is
used to calculate METG(50\%), as described in Section~\ref{sec:metg}. The
red, dashed line shows the point where 50\% efficiency is achieved.

@@

Implicitly parallel systems such as PaRSEC, StarPU and Regent that
rely on runtime analysis to build the DAG can suffer from
scalability bottlenecks if every node must consider the tasks
executing on all other nodes. PaRSEC DTD and StarPU mitigate this
partially by allowing the user to omit tasks that are not direct
dependencies of those executed on the current node. However, this DAG
trimming approach still requires some dynamic checks that scale with
the number of nodes and thus limits scalability. Approaches based on compile-time analysis can
partially or fully mitigate this overhead. PaRSEC PTG improves over DTD 
by performing DAG expansion at compile time~\cite{PARSEC_DTD}, but
still retains dynamic checks leading to limited scalability. Regent
uses a compile-time optimization that enables full horizontal
scalability~\cite{ControlReplication17}. A similar, manual
optimization is shown in the plots as PaRSEC DTD Shard.

@@

The difference between the remaining systems is due primarily to the
scheduling behavior of the various systems. The execution of 4
simultaneous task graphs partially, mitigate the
load imbalance in the tasks. Therefore, systems which provide an
additional on-node work stealing capability see additional gains in
efficiency at large task granularities. However, the use of
work-stealing queues can also impact throughput at very small task
granularities. This can be seen in the difference between Chapel
Distrib (which uses a work stealing scheduler) vs Chapel with its
default (non-work-stealing) scheduler.
